Agile Formality: A Mole of Software Verification Practices

### 2010-07-02 papers/ModelBasedTestCaseGenerationDataStreamProtocol/paper.tex
added small explanation of mole in abstract

  Members of the agile programming and formal methods communities do
  not always see eye-to-eye.  These two communities often do not talk
  to or learn from each other.  Only recently, as highlighted by the
  September 2009 issue of IEEE Software, the IFIP workshop on
  balancing agility and formalism in software engineering, and the
  first edition of the first international workshop for formal methods
  and agile methods, have ideas from the two communities begun to be
  synthesized.  While the problem-solving approaches and psychological
  attitudes of members of the two communities differ widely, we
  exploit this clash of viewpoints, synthesizing a new development
  processes that actually blends, rather than mashes together, best
  practices from the two worlds.  This paper summarizes our process
  and a supporting complex case study, showing that it is not only
  possible, but tasty, to combine the ``chili pepper'' of formal
  methods and the ``chocolate'' of agile programming, thus producing a
  tasty ``mole'' of software engineering practices.

@@

Agile and formal development methodologies, like oil and water,
usually do not blend together well.  This is because of several
reasons, the most important of which is often characterized as a
radical difference in psychological attitudes about software
development.

>>>>

  Members of the agile programming and formal methods communities do
  not always see eye-to-eye.  These two communities often do not talk
  to or learn from each other.  Only recently, as highlighted by the
  September 2009 issue of IEEE Software, the IFIP workshop on
  balancing agility and formalism in software engineering, and the
  first edition of the first international workshop for formal methods
  and agile methods, have ideas from the two communities begun to be
  synthesized.  While the problem-solving approaches and psychological
  attitudes of members of the two communities differ widely, we
  exploit this clash of viewpoints, synthesizing a new development
  processes that actually blends, rather than mashes together, best
  practices from the two worlds.  This paper summarizes our process
  and a supporting complex case study, showing that it is not only
  possible, but tasty, to combine the ``chili pepper'' of formal
  methods and the ``chocolate'' of agile programming, thus producing a
  tasty ``mole'' (as in the highly-spices Mexican sauce) of software
  engineering practices.

@@

Agile and formal development methodologies, like oil and water
usually do not blend together well.  This is because of several
reasons, the most important of which is often characterized as a
radical difference in psychological attitudes about software
development.
